---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DynamicStrategies

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/Reckziegel/DynamicStrategies/branch/main/graph/badge.svg)](https://codecov.io/gh/Reckziegel/DynamicStrategies?branch=main)
[![R-CMD-check](https://github.com/Reckziegel/DynamicStrategies/workflows/R-CMD-check/badge.svg)](https://github.com/Reckziegel/DynamicStrategies/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`DynamicStrategies` is currently on the development stage. 

## Installation

Install the development version from github with:

``` r
# install.packages("devtools")
install.packages("DynamicStrategies")
```

## Example

```{r}
library(DynamicStrategies)
library(ggplot2)

# Build a Convex Strategy
convex_strat <- simulate_strategy(strategy = "max_utility")
convex_strat


# See the main statistics
extract_stats(convex_strat)


# See the P&L simulation
autoplot(convex_strat)


# Stress-Test a parameter
plot_sensivities(strategy = convex_strat, variable = "allocation", from = 0, to = 1, size = 20)
```


## References

- Attilio Meucci (2021). Review of Dynamic Allocation Strategies (https://www.mathworks.com/matlabcentral/fileexchange/28384-review-of-dynamic-allocation-strategies), MATLAB Central File Exchange. Retrieved September 5, 2021.

- Meucci, Attilio, Review of Dynamic Allocation Strategies: Utility Maximization, Option Replication, Insurance, Drawdown Control, Convex/Concave Management (July 7, 2010). Available at SSRN: https://www.ssrn.com/abstract=1635982
